---
title: "Ece#7_Multivariate Adaptive Regression Splines"
output: html_document
---

```{r setup, include=FALSE}
# Helper packages
library(dplyr)     # for data wrangling
library(ggplot2)   # for awesome plotting

# Modeling packages
library(earth)     # for fitting MARS models
library(caret)     # for automating the tuning process
library(rsample)
# Model interpretability packages
library(vip)       # for variable importance
library(pdp)       # for variable relationships
```

#Data:
```{r}
library(ISLR)
data(Hitters)
set.seed(123)  # for reproducibility
Hitters = na.omit(Hitters)  ## clean dataset
split <- initial_split(Hitters, 0.7, strata = "Salary")
Hitters_train <- training(split)
Hitters_test <- testing(split)
```

# 1.Apply a MARS model with all features.

```{r}
mars1 <- earth(
  Salary ~ .,  
  data = Hitters_train   
)
# Print model summary
print(mars1)
```

# 2.How does the model performance compare to your previous models?

```{r}
hyper_grid <- expand.grid(
  nprune = seq(2, 50, length.out = 10) %>% floor(),
  degree = 1:3
)

# perform resampling


model <- train(
  Salary ~ ., 
  data = Hitters_train, 
  trControl = trainControl(method = "cv", number = 10),
  method = "earth", #<<
  tuneGrid = hyper_grid,
  metric = "RMSE")
  
  


model$bestTune
##    nprune degree
## 23     12      3
ggplot(model)
```

# 3.1.How many of the features are influential? 
```{r}


importance <- varImp(model, scale=FALSE)
print(importance)
plot(importance)
```

# 3.2. Which 10 features are considered most influential.
```{r}
p1 <- vip(model, num_features = 10, geom = "point", value = "gcv") + ggtitle("GCV")
plot(p1)
```

# 4.1. Does your model include hinge functions? If so, explain their coefficient 
```{r}
summary(mars1) %>% .$coefficients %>% head(10)
```

# 4.2. and plot their impact on the predicted response variable.

```{r}
plot(mars1, which = 1)
```

# 5. Does your model include interactions? If so, pick the interaction effect that is most influential and explain the coefficient.
```{r}
model$finalModel %>%
  coef() %>%  
  broom::tidy() %>%  
  filter(stringr::str_detect(names, "\\*")) 
```
