---
title: "K-nearest Neighbor"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)      # for data wrangling
library(ggplot2)    # for awesome graphics
library(rsample)    # for creating validation splits
library(recipes)    # for feature engineering

# Modeling packages
library(caret)       # for fitting KNN models
library(vip)      # for variable importance
library(ISLR)

```


# Using the ISLR::Default dataset where the default variable is the response variable:

```{r echo=FALSE}
data('Default')

set.seed(123)
split <- initial_split(Default , prop =.7 )
default_train <- training(split)
default_test <- testing(split)
```

# 1. Apply a KNN model with all features. Use a grid search to assess values of k ranging from 2-200 that seeks to optimize the “ROC” metric.
```{r echo=FALSE}


# Create a hyperparameter grid search
hyper_grid <- expand.grid(k = seq(2, 200, by = 2))

cv <- trainControl(
  method = "repeatedcv", 
  number = 10, 
  repeats = 5,
  classProbs = TRUE,                 
  summaryFunction = twoClassSummary
)

# Execute grid search
knn_default <- train(
 default ~.,
 data = default_train,
  method = "knn",
  tuneGrid = hyper_grid,
  preProc = c("center", "scale"),
  trControl = cv
)
knn_default

```

# 2. Plot the grid search performance.
```{r echo=FALSE}

ggplot(knn_default)
```

# 3. What value for K optimizes model performance? What does this tell you about your data?

```{r echo=FALSE}


blueprint <- recipe(default ~., data = train) %>%
  step_nzv(all_nominal())  %>%
  step_integer(JobInvolvement) %>%
  step_center(all_numeric(), -all_outcomes()) %>%
  step_scale(all_numeric(), -all_outcomes()) 
  

  
cv <- trainControl(
  method = "repeatedcv", 
  number = 10, 
  repeats = 5
)

# Fit knn model and perform grid search
knn_grid <- train(
 blueprint, 
 data = train,
  method = "knn", 
  trControl = cv, 
  tuneGrid = hyper_grid,
  metric = "ROC"
)

ggplot(knn_grid)
```

# 4. Plot the ROC curve for the optimal model.
```{r echo=FALSE}

ggplot(knn_grid)
```

# 5. Which 10 features are considered most influential? Are these the same features that have been influential in previous models?
```{r echo=FALSE}

importance <- vip(knn_default, num_features = 10)
```

